Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-01-19 PaperVictor.tex
Atendi comentarios de Dr. Mochán

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. In the present work, the
average reflectance $\braket{R}$ \notaL{No entiendo por qué insisten
  en no usar tipografía matemática para símbolos como $R$. Los
  símbolos de menor y mayor no corresponden a los de promediar.}. of PS-based mirrors is maximized within a wide
wavelength and angular range for different porosity contrasts. Optimization is
performed to maximize the reflectance for minimum  thickness of the structure in the
visible (Vis) and near infrarred (NIR) regions of the electromagnetic spectrum.   The
mirrors are designed \notaL{No entiendo para qué haber cambiado el
  modo de activo a pasivo; es mucho mejor el activo.} using \textit{chirped}-type structures and \textit{stacking}
sub-mirrors. The chirped structures are found to be more suitable for the Vis range,
while stacked sub-mirrors are found to be better for the NIR region. Design, fabrication
and testing of some optimized omnidirectional structures with less
than 100 pairs of layers \notaL{Quizás periods no sea correcto, pues
  no son periódicos} has
been demonstrated.
\end{abstract}

@@

For the analysis of the propagation of electromagnetic fields
through multilayer systems, we employ a variant of the transfer matrix
method based on the formalism of Puente-Díaz et al. \cite{Puente2020}.
Its advantage over other formally equivalent approaches
\cite{Mochan1987,Ortiz2020,Chavez2020} is that it allows a
numerically stable
calculation of the reflectance even of very large multilayer systems,
even in the presence of absorption.
We assume  the system has  variations only along the $z$ direction
and consider an incident linearly polarized beam of light
(either TE or TM polarization) that propagates throughout
the structure. The reflectance and transmittance are given by
$R=|r|^{2}$ and  $T=\beta \left\vert t\right\vert ^{2}$,
respectively, with \cite{Puente2020}
\begin{equation}
	r=\sigma \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
		M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
	t=\frac{2\zeta}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
\end{equation}%
where $Z_0$ and $Z_s$ are the surface impedances of vacuum
and substrate, respectively, $\beta =\text{Re}Z_{0}/\text{Re}Z_{s}$,
$\sigma=-1$ and
$\zeta =Z_s$ for
TE polarization, while $\beta=\text{Re}Z_{s}/
\text{Re}Z_{0}$, $\sigma=+1$, and $\zeta =Z_0$ for TM
polarization.
Here, $M_{ij}$ are the elements
of the reconstructed transfer matrix
\begin{equation}
\resizebox{\textwidth}{!}{$\displaystyle{
	M=\frac{1}{Z^{+}-Z^{-}} \left(
	\begin{array}{cc}
		Z^{+}\text{exp}\left( iKD\right) -Z^{-}\text{exp}\left( -iKD\right)  &
		-2iZ^{+}Z^{-}\sin KD \\
		2i\sin KD & Z^{+}\text{exp}\left( -iKD\right) -Z^{-}\text{exp}\left(
		iKD\right)
	\end{array}%
	\right) \text{.}}$}
\label{MsBloch}
\end{equation}
which relates the electromagnetic fields at the substrate to those at
the surface,
Here, $Z^{\pm }$ are the surface impedances of the multilayered system
for fields propagating toward the substrate ($+$) or towards vacuum
($-$), and are given by
\begin{equation}
	Z^{\pm }=-\frac{\widetilde{M}_{12}}{\widetilde{M}_{11}-\Lambda _{\pm }}\text{,}  \label{ZBloch}
\end{equation}%
where
\begin{equation}
	\Lambda _{-}=\frac{1}{2}\text{Tr}\,\widetilde{M}\pm
        i\sqrt{1-\left( \text{Tr}\,\widetilde{M}/2\right)
		^{2}}\text{,}  \label{LBloch}
\end{equation}%
is chosen to satisfy the inequality $\left\vert \Lambda
_{-}\right\vert >1$, and $\Lambda _{+}=1/\Lambda _{-}$, and Tr denotes
the trace. $\widetilde{M}$ denotes the usual transfer matrix
\begin{equation}
	\widetilde{M} = \prod \limits_{j=1}^{N}%
	\begin{pmatrix}
		\cos k_{j}d_{j} & iZ_{j}\sin k_{j}d_{j} \\
		iY_{j}\sin k_{j}d_{j} & \cos k_{j}d_{j}%
	\end{pmatrix}%
	\label{Mcoef}
\end{equation}%
of the multilayered system, where
\begin{equation}
	k_{j}=\sqrt{\epsilon _{j}q^{2}-Q^{2}}  \label{kj}
\end{equation}%
is the normal component of the wave vector whithin the $j$-th layer, $Z_{j}$ is
its surface impedance, $Y_{j}=1/Z_{j}$ its surface
admittance, $\epsilon _{j}=n_{j}^{2}$ its permitivity (for simplicity we
assumed all media were nonmagnetic, with permeability $\mu _{i}=1$),
$q=\omega /c=2\pi /\lambda $ is the free-space wavenumber corresponding to
the wavelength $\lambda $ and
\begin{equation}
	Q=n_{0}q\sin \theta _{i}  \label{Snell}
\end{equation}%
is the projection of wavevector onto the interfaces,
which is conserved according to Snell's law, with
$\theta _{i}$ the angle of incidence. The surface
impedances are given by $Z_{j}=q/k_{j}$ for TE
polarization and $Z_{j}=k_{j}/q\epsilon _{j}$ for
TM polarization. The complex refractive index of the porous layers were
obtained through the Bruggeman's effective medium
theory, which has been reported to adequately reproduce
the PS optical parameters \cite{Giusseppe2011,Pap2006,Estrada2018}.

\notaL{Creo que no se ha explicado el proceso de diseño. No sé para
  qué damos tanto detalle sobre cómo se calculó, dado que todo está en
  la referencia.}
\section{Experimental details}\label{s:exp}

@@

\notaL{Aquí quitaron un comentario mío. ¿Ya no es relevante? ¿Ya se
  explicó cómo se hizo el diseño?}
\subsection{Chirped-type Bragg mirrors}\label{ss:chirped}

@@

The function
$f_{3}$ yields after optimization the highest $\braket{R}$ in the
region $\mathcal R_1$ with the thinnest structure (see table
\ref{tab:tableA}). Furthermore, this structure has a calculated OD gap
\notaL{I'm unsure about the nomenclature ``gap''. I guess it is
  theoretical, right?}
of 250 nm centered at 1125 nm with a
reflectance
$R>0.90$, as shown in Fig. \ref{Fig1}(b). We
synthesized a structure  designated {\em sample $S_1$} corresponding
to these results. For the region $\mathcal R_2$ the
resulting structures have similar thicknesses and attain similar reflectance
spectra, though the one with the smallest thickness and the maximum
reflectance is that obtained from the family $f_{1}$. We
also synthesized the corresponding
structure and designated it {\em sample $S_2$}. The
calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
This structure has a very wide region where $ R(\lambda, \theta)>
0.90$, which goes from 850 to 3000 nm in an angular range
from $0^\circ$ to $70^\circ$. Thus, it has a
quasi-OD (q-OD) gap of 2150 nm centered at 1925 nm.
The functions $f_i$ optimized for the region $\mathcal R_1$ are shown
in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
in Fig. \ref{Fig1}(c). The profiles $f_i$ are qualitatively
similar. For example, for $\mathcal R_1$ the optimal photonic
structures have a small number of periods tuned to the wavelengths where
silicon has a large absorption, i.e.,  the first periods of the
structure. For $\mathcal R_2$ it is only necessary that the periods
have an adequate ordering. \notaL{No entendí qué hay que comentar en
  este caso}
\begin{figure}
  \label{Fig1}
  \begin{center}
    \includegraphics[width=\textwidth]{F1Alternativa.pdf}
  \end{center}
  \caption{Profiles of the functions $f_n(\chi_j)$ optimized for
    the region $\mathcal R_1$ from 350 to 1400 nm (panel a) and
    $\mathcal R_2$ from 400 to 3000 nm (panel c). Reflectance
    for non-polarized light
    vs. wavelength and angle of incidence of the structure
    optimized for the region $\mathcal R_1$ (panel b) and
    $\mathcal R_2$ (panel d). The dotted lines
    delimit the area where $R> 90\%$ and the dashed lines
    indicate the quasi-OD region. In the first region there is
    an OD gap and in the second region there is a quasi OD
    gap.}
\end{figure}

We measured the reflectance spectra of samples $S_1$ and $S_2$
at various angles of incidence $\theta$. Due to
experimental limitations, we restrict our results to the case of
unpolarized light. In Fig. \ref{Fig2}(a), the calculated and measured
reflectance corresponding to sample $S_1$ are compared from 350 to 1400 nm for different angles of
incidence ($\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
$50^\circ$, and $60^\circ$). The spectra are qualitatively similar,
and for $\lambda>700$ nm and
$10^\circ < \theta < 40^\circ$, they agree quantitatively, with a
difference smaller than $5\%$. \notaL{Yo no veo nada especial en 40 grados: and for
$\theta > 40^\circ$ both spectra are qualitatively consistent}  The
measured reflectance is lower than the calculated one, more so at
small wavelengths and large angles. This difference
may be partially attributed to the scattering of light due to the
roughness present at the sample
\cite{Theiss1994,Chavez2020,Ortiz2020} that we have not taken into
account in our theory. Due to the limitations of our
spectrophotometer, we couldn't perform measurements for $\theta>60^\circ$ and thus
check the OD gap. Nevertheless, our results allow us to conclude that
the structure has a quasi-omni-directional
bandgap (R$\left(\lambda,\theta \right)>0.90$) between 980 and
1340 nm.
\begin{figure}
	\label{Fig2}
	\begin{center}
		\includegraphics[width=\textwidth]{F2Alternativa.pdf}
	\end{center}
	\caption{Reflectance spectra for non-polarized light calculated and measured at different
	angles of incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$,
        $40^\circ$, $50^\circ$, and $60^\circ$ for structure $S_1$
        (panel a)  and $S_2$ (panel b). The gray band indicates the
        region where the reflectance is greater than  $0.90$,
        corresponding to the quasi OD gap of the
        structure. Inset: photograph of the synthesized structure.}
\end{figure}
In Fig. \ref{Fig2}(b) we compare the
calculated and measured spectra of sample $S_2$ in the range
from 400 to 3000 nm.
Both spectra are very similar, with some differences at long
wavelengths which can be
attributed to an increase of imperfections such as wavy layers and
more roughness for deeper layers, due to a more restricted diffusivity
of the electrolyte as the thickness of the structure is increased
\cite{Negro2003,Vincent1993}. According to our results, this
structure has a wide quasi-omnidirectional gap ($R>0.90$) of 1800 nm
centered at 1880 nm.

@@

Another class of techniques for designing good reflectors across a wide spectral range
is to stack sub-mirrors tuned to different wavelengths chosen with
different criteria. For
example, Agarwal et al. \cite{Agarwal2003} proposed to stack sub-mirrors as follows:
tune the first sub-mirror to certain wavelength $\lambda_{1}$. Tune
subsequent submirrors $j$ to wavelengths $\lambda_j$, chosen so that $\lambda_{j+1} +
\lambda_{j}=2+j$ \notaL{This cannot be correct. Please check}. Furthermore, Estrada-Wiese et al. \cite{DelRio2018}
developed a method that combines three stochastic optimization algorithms together with
a  narrow space search methodology to obtain a customized and optimized
PC configuration.

We recall that for a periodic structure, the propagation of
electromagnetic waves is described by the dispersion relation
\begin{equation}
	 \cos (KD) = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
\end{equation}
where $K$ is Bloch's vector, $\bm M$ the transfer matrix of a single
period of thickness $D$ \cite{Mochan1987, Mochan1988,
  Perez2018}. \notaL{Tr was already defined and the reference to the
  equation is wrong:  denotes the trace
and $M$ is the matrix given by Eq. \ref{MsBloch}}. Thus,
whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
electromagnetic energy cannot propagate in the periodic system and we
expect a high reflectance for a finite system made of a finite number
of periods. This suggests the following design. We stack submirrors
each made of a few periods of a periodic system such that its photonic band gap
(PBG) overlaps the PBG of the previous and that of the next
submirror. The number of periods of each sub-mirror is an
important parameter. If it is too small, the sub-mirror would be
partially transparent within the PBG. If it is too large, the
resulting structure would be too thick. We followed two design
strategies: In the first, we considered sub-mirrors each with the same
number of periods. In the second, a different number of periods was
assigned to each submirrors with a PBG center within different
spectral regions: we used a single period for
$\lambda_{D}<500$ nm, two periods for $500 <\lambda_ {D} < 650$ nm
and three periods for $650<\lambda_ {D}<800$ nm.  and for
$\lambda_{D}>800$ nm, the number of periods was variable.\notaL{No se
  entiende. Los números uno, dos, tres ¿se sacaron de la manga? ¿se
  optimizaron? Para <800, ¿de dónde se sacó el número de periodos?}
In both
designs, the optimal overlap of two consecutive PBGs was obtained that
maximized reflectance.\notaL{No quisiste decir average reflectance
  $\braket{R}$?. Si sí, en qué rango promediaste?}
Reflectance spectra were calculated for
$400\text{nm}\le \lambda\le 3000\text{nm}$ and for $0^\circ\le\theta\le90^\circ$.

Table \ref{tab:table2} shows the number of periods of each sub-mirror
($Np_{se}$),\notaL{Está difícil esta notación. ¿De dónde vienen la s y
  la e. $Np_{se}$ parece el producto de $N$ con $p_{se}$. ¿De dónde la
  p?} the total number of stacked sub mirrors ($N_{se}$)
\notaL{El encabezado de la tabla está mal}, the
thickness of the structure, the optimal overlap of two consecutive
PBGs and the average reflectance. The first block corresponds to
sub-mirrors with a constant number of periods, while the second block
corresponds to sub-mirrors with a variable number of periods according
to the design wavelength.\notaL{No entiendo nada: qué dejaste fijo y
  qué permitiste variar para optimizar en cada bloque de la tabla?}
\begin{table}[htbp]
  \begin{center}
    \caption{Parameters that maximize $\braket{R}$ for  stacked sub-mirrors.}
    \label{tab:table2}
    \begin{tabular}{|c|c|c|c|c|}
      \hline % <-- Toprule here
      \textbf{$Np_{se}$}&{\textbf{$Np_{se}$}} &\textbf{Thickness}&\textbf{Overlap}&$\braket{R}$\\
			&&($\mu$m)& \textbf{PBG $\%$}&$\%$\\
      \hline
      1&98&43.2&95&91.0\\
      3&31&42.5&81&91.8\\
      5&17&41.9&68&92.0\\
      \hline
      4&25&38.7&74&92.3\\\textcolor{red}{6}&\textcolor{red}{18}&\textcolor{red}{41.5} &\textcolor{red}{78} & \textcolor{red}{95.35}\\
      10&13&45.4&56&95.34\\
      \hline
    \end{tabular}
  \end{center}
\end{table}

According to table \ref{tab:table2}, the structure that has the highest
reflectance is in the second block, with an optimal overlap between
consecutive PBGs of $78\%$, a thickness of
41.5 $\mu$m, and  average reflectance $\braket{0.953}$. It is made up
of 18 sub-mirrors tuned to the following wavelengths
400, 460, 510, 570, 640, 720,810,910, 1020, 1150, 1290, 1450, 1630,
1830, 2060, 2320, 2610, and 2860 nm.
We synthesized this structure and designated it {\em sample $S_3$}.
Its calculated and measured
reflectance spectra are shown in Fig. \ref{Fig3}.
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]
{F3Alternativa.pdf}
\end{center}
\caption{ (a) Calculated reflectance $R(\lambda,\theta)$ for non-polarized light of the optimized structure $S_3$
  as a function of wavelength $\lambda$ and incidence angle
  $\theta$. (b) Measured and calculated reflectance spectra at several
  angles of incidence $\theta=10^\circ$, $20^\circ$,
  $30^\circ$, $40^\circ$, $50^\circ$, $60^\circ$. The gray band indicates
  the region in which the reflectance is greater than $R>0.90$.  Inset shows a
  photograph with a top view of the synthesized structure.}
\label{Fig3}
\end{figure}

Fig. \ref{Fig3}(a) reveals a quasi omnidirectional
mirror in the range from 950 to 2900 nm, with an angular range between $0^\circ$ and
$60^\circ$. It is also observed that at incidence angles $\theta
>70^\circ$ and long
wavelengths the reflectance decreases and has oscillations, which are attributed to the
greater penetration of the electromagnetic field within the structure, as shown by
Puente-D\'{\i}az, et al. \cite{Puente2020}. In Fig. \ref{Fig3}(b) we compare the
calculated and measured reflectance for the structure $S_3$ at several angles of
incidence. Although, the quasi omnidirectional wavelength range of the synthesized
structure is slightly smaller than the calculated one, from 950 to 2750 nm, the measured
PBG is almost twice as wide as a recently reported PS chirped
structure \cite{Chavez2020}. \notaL{Por qué comparamos con ésta? ¿Era
  la mejor que había? Habría que decirlo}

>>>>

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. In the present work, the
average reflectance $\braket{R}$ \notaL{No entiendo por qué insisten
  en no usar tipografía matemática para símbolos como $R$. Los
  símbolos de menor y mayor no corresponden a los de promediar.}
\notaV{Fue un error mio. No habia agregado el paquete "braquet"}. of PS-based mirrors is maximized within a wide
wavelength and angular range for different porosity contrasts. Optimization is
performed to maximize the reflectance for minimum  thickness of the structure in the
visible (Vis) and near infrarred (NIR) regions of the electromagnetic spectrum. We design the
mirrors  \notaL{No entiendo para qué haber cambiado el
  modo de activo a pasivo; es mucho mejor el activo.} 
\notaV{Cambie la oracion a voz activa} using \textit{chirped}-type structures and \textit{stacking}
sub-mirrors. The chirped structures are found to be more suitable for the Vis range,
while stacked sub-mirrors are found to be better for the NIR region. Design, fabrication
and testing of some optimized omnidirectional structures with less
than 100 pairs of layers \notaL{Quizás periods no sea correcto, pues
  no son periódicos} has
been demonstrated.
\end{abstract}

@@

\notaV{Regreso el parrafo de la primera versi\'{o}n}

For the analysis of the propagation of electromagnetic fields through
multilayer systems it is usual to employ the transfer matrix
method \cite{PerezA2004,Pochi2005} \notaL{reference}. Assuming the system is 1D, with variations
only along the $z$ directions, and that the polarization of light is either
transverse electric (TE) or transverse magnetic (TM), the
transfer matrix $M\left(z_{2},z_{1}\right)$ is
a 2x2 matrix that relates the components of the electric $E_{\| }$
and magnetic  $H_{\|}$ fields parallel to the $xy$ plane
evaluated at $z_2$ to their value at $z_{1}$,
\begin{equation*}
	\left(
	\begin{array}{c}
		E_{\|} \\
		H_{\| }%
	\end{array}%
	\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
	\begin{array}{c}
		E_{\| } \\
		H_{\| }%
	\end{array}%
	\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain and use $M$
\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
for the numerically stable calculation of the reflectance of large
multilayer systems, as
proposed by Puente-Díaaz, et al. \cite{Puente2020}, summarized in the
supplementary information. The
explicit expressions for the optical coefficients are:
\begin{equation}
	r=\mp \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
		M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
	t=\frac{2Z_{\alpha
	}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
\end{equation}%
where $M_{ij}$ are the elements
of the transfer matrix which transfer
the fields from its surface interface with vacuum at $z_0$ towards the
substrate at $z_s$,  $Z_0$ is the surface impedance of vacuum and $Z_s$ is the
surface impedance of the substrate, and we define $r=F_r/F_i$ and $t=F_t/F_i$ in terms
of the reflected and transmitted fields, where we choose the $F$'s as electric
fields for (TE) polarization and magnetic fields
for transverse magnetic polarization (TM). The upper sign $-$ in
Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization, respectively.
The reflectance is given by
$R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=\text{Re}Z_{0}/\text{Re}Z_{s}$ for TE polarization and $\beta =\text{Re}Z_{s}/\text{Re}Z_{0}$ for
TM polarization. The complex refractive index of the porous
layers were obtained through the Bruggeman's effective medium theory, which
has been reported to adequately reproduce the PS optical parameters
\cite{Giusseppe2011,Pap2006,Estrada2018}.

\notaL{Creo que no se ha explicado el proceso de diseño. No sé para
  qué damos tanto detalle sobre cómo se calculó, dado que todo está en
  la referencia.}

\section{Experimental details}\label{s:exp}

@@

\notaL{Aquí quitaron un comentario mío. ¿Ya no es relevante? ¿Ya se
  explicó cómo se hizo el diseño?}

\notaV{En el siguiente parrafo se explican los procesos de diseño}

\subsection{Chirped-type Bragg mirrors}\label{ss:chirped}

@@

The function
$f_{3}$ yields after optimization the highest $\braket{R}$ in the
region $\mathcal R_1$ with the thinnest structure (see table
\ref{tab:tableA}). Furthermore, this structure has a calculated OD gap
\notaL{I'm unsure about the nomenclature ``gap''. I guess it is
  theoretical, right?}
 \notaV{Podr\'{i}a utilizar el t\'{e}rmino "OD width" para referirme al ancho omnidireccional del espejo}
of 250 nm centered at 1125 nm with a
reflectance
$R>0.90$, as shown in Fig. \ref{Fig1}(b). We
synthesized a structure  designated {\em sample $S_1$} corresponding
to these results. For the region $\mathcal R_2$ the
resulting structures have similar thicknesses and attain similar reflectance
spectra, though the one with the smallest thickness and the maximum
reflectance is that obtained from the family $f_{1}$. We
also synthesized the corresponding
structure and designated it {\em sample $S_2$}. The
calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
This structure has a very wide region where $ R(\lambda, \theta)>
0.90$, which goes from 850 to 3000 nm in an angular range
from $0^\circ$ to $70^\circ$. Thus, it has a
quasi-OD (q-OD) gap of 2150 nm centered at 1925 nm.
The functions $f_i$ optimized for the region $\mathcal R_1$ are shown
in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
in Fig. \ref{Fig1}(c). The profiles $f_i$ are qualitatively
similar. For example, for $\mathcal R_1$ the optimal photonic
structures have a small number of periods tuned to the wavelengths where
silicon has a large absorption, i.e.,  the first periods of the
structure. 
\notaV{replanteo la idea: "For $\mathcal R_2$ it is only necessary that the periods have an adequate ordering.}
\notaL{No entendí qué hay que comentar en
  este caso} 
Due in $\mathcal R_2$, the absorption of porous silicon is negligible, the periods are distributed quasi-evenly.

\begin{figure}
  \label{Fig1}
  \begin{center}
    \includegraphics[width=\textwidth]{F1Alternativa.pdf}
  \end{center}
  \caption{Profiles of the functions $f_n(\chi_j)$ optimized for
    the region $\mathcal R_1$ from 350 to 1400 nm (panel a) and
    $\mathcal R_2$ from 400 to 3000 nm (panel c). Reflectance
    for non-polarized light
    vs. wavelength and angle of incidence of the structure
    optimized for the region $\mathcal R_1$ (panel b) and
    $\mathcal R_2$ (panel d). The dotted lines
    delimit the area where $R> 90\%$ and the dashed lines
    indicate the quasi-OD region. In the first region there is
    an OD gap and in the second region there is a quasi OD
    gap.}
\end{figure}

We measured the reflectance spectra of samples $S_1$ and $S_2$
at various angles of incidence $\theta$. Due to
experimental limitations, we restrict our results to the case of
unpolarized light. In Fig. \ref{Fig2}(a), the calculated and measured
reflectance corresponding to sample $S_1$ are compared from 350 to 1400 nm for different angles of
incidence ($\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
$50^\circ$, and $60^\circ$). The spectra are qualitatively 
similar, and for $\lambda>700$ nm and $10^\circ < \theta < 
40^\circ$, they agree quantitatively, with a difference smaller 
than $5\%$.
\notaL{Yo no veo nada especial en 40 grados: and for
$\theta > 40^\circ$ both spectra are qualitatively consistent} \notaV{De acuerdo. Se puede omitir}
The
measured reflectance is lower than the calculated one, more so at
small wavelengths and large angles. This difference
may be partially attributed to the scattering of light due to the
roughness present at the sample
\cite{Theiss1994,Chavez2020,Ortiz2020} that we have not taken into
account in our theory. Due to the limitations of our
spectrophotometer, we couldn't perform measurements for $\theta>60^\circ$ and thus
check the OD gap. Nevertheless, our results allow us to conclude that
the structure has a quasi-omni-directional
bandgap (R$\left(\lambda,\theta \right)>0.90$) between 980 and
1340 nm.
\begin{figure}
	\label{Fig2}
	\begin{center}
		\includegraphics[width=\textwidth]{F2Alternativa.pdf}
	\end{center}
	\caption{Reflectance spectra for non-polarized light calculated and measured at different
	angles of incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$,
        $40^\circ$, $50^\circ$, and $60^\circ$ for structure $S_1$
        (panel a)  and $S_2$ (panel b). The gray band indicates the
        region where the reflectance is greater than  $0.90$,
        corresponding to the quasi OD gap of the
        structure. Inset: photograph of the synthesized structure.}
\end{figure}
In Fig. \ref{Fig2}(b) we compare the
calculated and measured spectra of sample $S_2$ in the range
from 400 to 3000 nm.
Both spectra are very similar, with some differences at long
wavelengths which can be
attributed to an increase of imperfections such as wavy layers and
more roughness for deeper layers, due to a more restricted diffusivity
of the electrolyte as the thickness of the structure is increased
\cite{Negro2003,Vincent1993}. According to our results, this
structure has a wide quasi-omnidirectional gap ($R>0.90$) of 1800 nm
centered at 1880 nm.

@@

Another class of techniques for designing good reflectors across a wide spectral range
is to stack sub-mirrors tuned to different wavelengths chosen with
different criteria. 
\notaV{I rewrote this "For example, Agarwal et al. 
	\cite{Agarwal2003} proposed to stack sub-mirrors as follows: 
	tune the first sub-mirror to certain wavelength $\lambda_{1}$. 
	Tune subsequent submirrors $j$ to wavelengths $\lambda_j$, 
	chosen so that $\lambda_{j+1} + \lambda_{j}=2+j$."} 
For example, Agarwal et al. \cite{Agarwal2003} proposed a photonic 
structure in which she stacked 54 sub-mirrors as follows: the 
first sub-mirror consisted of 2.5 periods and tuned it to 
$\lambda_{1}=700$ nm; the following sub-mirrors were tuned to the 
wavelengths $\lambda_{j}$ according to the sequence $\lambda_{j+1} 
+ \lambda_{j}=2+j$ with 4 periods for each of the following 
periods.
\notaL{This cannot be correct. Please check}. Furthermore, Estrada-Wiese et al. \cite{DelRio2018}
developed a method that combines three stochastic optimization algorithms together with
a  narrow space search methodology to obtain a customized and optimized
PC configuration.

We recall that for a periodic structure, the propagation of
electromagnetic waves is described by the dispersion relation
\begin{equation}
	 \cos (KD) = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
\end{equation}
where $K$ is Bloch's vector, $\bm M$ the transfer matrix of a single
period of thickness $D$ \cite{Mochan1987, Mochan1988,
  Perez2018}. \notaL{Tr was already defined and the reference to the
  equation is wrong:  denotes the trace
and $M$ is the matrix given by Eq. \ref{MsBloch}}. \notaV{Entendido, gracias} Thus,
whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
electromagnetic energy cannot propagate in the periodic system and we
expect a high reflectance for a finite system made of a finite number
of periods. This suggests the following design. We stack submirrors
each made of a few periods of a periodic system such that its photonic band gap
(PBG) overlaps the PBG of the previous and that of the next
submirror. The number of periods of each sub-mirror is an
important parameter. If it is too small, the sub-mirror would be
partially transparent within the PBG. If it is too large, the
resulting structure would be too thick. We followed two design
strategies: In the first, we considered sub-mirrors each with the same
number of periods. In the second, a different number of periods was
assigned to each submirrors with a PBG center within different
spectral regions: we used a single period for
$\lambda_{D}<500$ nm, two periods for $500 <\lambda_ {D} < 650$ nm
and three periods for $650<\lambda_ {D}<800$ nm.  and for
$\lambda_{D} \geq 800$ nm, the number of periods was variable.
\notaL{No se entiende. Los números uno, dos, tres ¿se sacaron de la manga? ¿se optimizaron? Para <800, ¿de dónde se sacó el número de periodos?}
\notaV{Los números de periodos uno, dos, tres, los eleg\'{i} para 
	que la estructura tenga pocos periodos en la region visible. 
	Adem\'{a}s, del c\'{a}lculo de las Trazas y reflectancias de 
	los subespejos individuales sintonizados de 1000 a 2500 nm, 
	tambi\'{e}n tienen una regi\'{o}n de propagaci\'{o}n prohibida 
	en el intervalo de 400 a 900 y la reflectancia es mayor al 
	80\%. Esto se puede observar en la Fig. SITrazasyRefSE.pdf}
In both designs, the optimal overlap of two consecutive PBGs was obtained that maximized reflectance.
\notaL{No quisiste decir average reflectance $\braket{R}$?. Si sí, en qué rango promediaste?} \notaV{Si, se promedi\'{o} en el siguiente rango}
Reflectance spectra were calculated for
$400\text{nm}\le \lambda\le 3000\text{nm}$ and for $0^\circ\le\theta\le90^\circ$.

Table \ref{tab:table2} shows the number of periods of each sub-mirror ($p$),
\notaL{Está difícil esta notación. ¿De dónde vienen la s y
  la e. $Np_{se}$ parece el producto de $N$ con $p_{se}$. ¿De dónde la p?} \notaV{Lo cambi\'{o} por $p$ de periods y $N$ de N\'{u}mero total de periodos}
the total number of stacked sub mirrors ($N_{se}$)
\notaL{El encabezado de la tabla está mal} \notaV{Corregido}, the
thickness of the structure, the optimal overlap of two consecutive
PBGs and the average reflectance. The first block corresponds to
sub-mirrors with a constant number of periods, while the second block
corresponds to sub-mirrors with a variable number of periods according
to the design wavelength. \notaL{No entiendo nada: qué dejaste 
	fijo y qué permitiste variar para optimizar en cada bloque de la tabla?}
\notaV{En el primer bloque \'{u}nicamente se optimiz\'{o} el traslape de dos PBGs consecutivos. En el segundo bloque, se optimizaron el n\'{u}mero de periodos (de 4 a 10 periodos) de los subespejos sintonizados a $\lambda_{D} \geq 800$ nm y el traslape de dos PBGs consecutivas.} 
\begin{table}[htbp]
  \begin{center}
    \caption{Parameters that maximize $\braket{R}$ for  stacked sub-mirrors.}
    \label{tab:table2}
    \begin{tabular}{|c|c|c|c|c|}
      \hline % <-- Toprule here
      \textbf{$p$}&{\textbf{$N$}} &\textbf{Thickness}&\textbf{Overlap}&$\braket{R}$\\
			&&($\mu$m)& \textbf{PBG $\%$}&$\%$\\
      \hline
      1&98&43.2&95&91.0\\
      3&31&42.5&81&91.8\\
      5&17&41.9&68&92.0\\
      \hline
      4&25&38.7&74&92.3\\\textcolor{red}{6}&\textcolor{red}{18}&\textcolor{red}{41.5} &\textcolor{red}{78} & \textcolor{red}{95.35}\\
      10&13&45.4&56&95.34\\
      \hline
    \end{tabular}
  \end{center}
\end{table}

According to table \ref{tab:table2}, the structure that has the highest
reflectance is in the second block, with an optimal overlap between
consecutive PBGs of $78\%$, a thickness of
41.5 $\mu$m, and  average reflectance $\braket{0.953}$. It is made up
of 18 sub-mirrors tuned to the following wavelengths
400, 460, 510, 570, 640, 720, 810, 910, 1020, 1150, 1290, 1450, 
1630, 1830, 2060, 2320, 2610, and 2860 nm.
We synthesized this structure and designated it {\em sample $S_3$}.
Its calculated and measured
reflectance spectra are shown in Fig. \ref{Fig3}.
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]
{F3Alternativa.pdf}
\end{center}
\caption{ (a) Calculated reflectance $R(\lambda,\theta)$ for non-polarized light of the optimized structure $S_3$
  as a function of wavelength $\lambda$ and incidence angle
  $\theta$. (b) Measured and calculated reflectance spectra at several
  angles of incidence $\theta=10^\circ$, $20^\circ$,
  $30^\circ$, $40^\circ$, $50^\circ$, $60^\circ$. The gray band indicates
  the region in which the reflectance is greater than $R>0.90$.  Inset shows a
  photograph with a top view of the synthesized structure.}
\label{Fig3}
\end{figure}

Fig. \ref{Fig3}(a) reveals a quasi omnidirectional
mirror in the range from 950 to 2900 nm, with an angular range between $0^\circ$ and
$60^\circ$. It is also observed that at incidence angles $\theta
>70^\circ$ and long
wavelengths the reflectance decreases and has oscillations, which are attributed to the
greater penetration of the electromagnetic field within the structure, as shown by
Puente-D\'{\i}az, et al. \cite{Puente2020}. In Fig. \ref{Fig3}(b) we compare the
calculated and measured reflectance for the structure $S_3$ at several angles of
incidence. Although, the quasi omnidirectional wavelength range of the synthesized
structure is slightly smaller than the calculated one, from 950 to 2750 nm, the measured
PBG is almost twice as wide as a recently reported PS chirped
structure \cite{Chavez2020}. \notaL{Por qué comparamos con ésta? 
	¿Era la mejor que había? Habría que decirlo}
\notaV{S\'{i}, es la estructura, a base de SP, que tiene el mayor ancho OD}
